Stereo odometry based on Local Intensity Order Pattern

### 2015-05-12 llncs2e/main.tex
springer template started

% Template for ICIP-2015 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}

\usepackage{spconf,amsmath,graphicx}
\usepackage{caption}

@@

% Title.
% ------
\title { On Deep Convolutional networks for large scale image classification}
%
% Single address.
% ---------------
\name{Mahesh C., Student Member, IEEE, Madhu S. Nair, Member, IEEE}
\address{Department of Computer Science, University of Kerala, Kariavattom\\ Thiruvananthapuram-695581,
	Kerala, India.
}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%

@@

\subsection{Network in Network }
Inspired by the work of Ian J. Goodfellow et al.\cite{Goodfellow2013} on max out networks,  Min Lin et al. \cite{Lin2013} introduced a micro-network in each convolution layer so that it will compute more abstract features.This network gave a state-of-the-art performance in  ILSVRC 2013 competition with an error rate of 12.95\%.They used NVIDIA TITAN GPU to train the network. Using multilayer perceptron instead of voting to approximate convex functions of each  local patches may result in a good accuracy; but this is equivalent to moving linear separability problem into another hyperspace. So, if the input is in high frequency, this will end up in modeling large number of hidden layers and make the network structure more dependent on the problem. It will diverge the idea of the convolution network from \emph{learn anything} to a \emph{local search}.

@@

\bibliographystyle{IEEEbib}
\bibliography{refs}

\end{document}% Template for ICIP-2015 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
explores better feature extraction, feature coding, and classification.  The purpose of this paper is to review the application of supervised  deep convolution networks in this field. Numerous techniques have been reported to improve the performance of the convolution networks. Experimental analysis shows that with a large amount of labeled data, convolution networks can learn very complex functions such as image classification.

\par In the visual cortex, perception cells are in the  order, simple$\Longrightarrow$complex$\Longrightarrow$lower-order-hypercomplex$\Longrightarrow$higher-order-hypercomplex. Activation of  a lower stage is  influenced by  the position of the input patterns, and  higher stages are  position-invariant. There are several  contradictory to this structure, but no one   completely deny this hierarchical model.
\par Inspired by this work, Fukushima, K \cite{Stark1980} proposed a neural network model for pattern recognition called neocognitron.
In neocognitron, cells are arranged in  a number of  cascaded structure. Each  structure $U$ include a  simple cell layer $U_s$ and a complex cell layer $U_c$. This network is not affected by change in position or small distortion in the shape of patterns.  It is also capable of doing self-organization based on an unsupervised competitive learning algorithm \cite{Fukushima1982} in the first two layers and classification based on  supervised learning in the output layer.
\begin{figure}[ht]
 \centering
 \includegraphics[width=8cm]{Figures/neocognitron.eps}
\caption{Neocognitron}
\label{neo}
\end{figure}
\section{Convolutional Networks}
\par Neocognitron was improved by  Yann LeCun \cite{lecun-86}, \cite{lecun-89e}, using backpropagation algorithm  to train the entire system. It uses local receptive fields, share weights and  sub-sampling to achieve  shift, position and distortion invariance. A typical Convolutional Network called  LeNet-5 was proposed by   Yann LeCun et al. \cite{LeCun1998}  for document recognition. Using \allowbreak local receptive fields, network can extract elementary visual features such as edges, end points and corners. These features will be combined to obtain high order features in the following layers. Elementary feature detectors with identical weights can be useful in different parts of the image. So the units with  the same set of weights are arranged in plane, and output from  the units of a plane is called  a feature map. Units in  a feature map perform the same operation on different parts of the same image. A convolution layer is composed of the set of feature maps with differently weighed units. In the implementation, a unit in the feature map scans the image and store the states in the feature map. This operation is equivalent to convolution with a kernel composed of a  set of weights and image.

 \includegraphics[width=8cm]{Figures/convent.eps}
\caption{A typical convolutional network architecture }
\label{net}
\end{figure}
\emph{Filter Bank Layer:} This layer computes $y_{j}$ the convolution between an input feature map   $x_i$ and trainable filter kernel $k_{ij}$ 
 ie. $y_j=b_j+\sum_i {k_{ij}*x_i}$, where $b_j$ is a trainable bias, $i$ and $j$ are  array indices, and $*$ is the convolution operator.\\
\emph{Non-Linearity Layer:} This layer applies a non-linearity function such as $tanh(x)$ or $(1+e^{-x})^{-1}$ to unit output. But to reduce training time with gradient descent, new implementations uses the function $max(0,x)$. Units with this non-linearity is called Rectified Linear Units (ReLUs) \cite{Nair2010}.\\
\emph{Feature Pooling Layer:} It  reduces the dimension of  feature map by applying the techniques like averaging or max-pooling.

% -------------------------------------------------------------------------

\begin{figure}[t]

\begin{minipage}[b]{.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{Figures/org}}
%  \vspace{2.0cm}
  \centerline{Input image}\medskip
\end{minipage}
%
\begin{minipage}[b]{.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{Figures/first}}
%  \vspace{1.5cm}
  \centerline{Output - first component }\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{0.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{Figures/second}}
%  \vspace{1.5cm}
  \centerline{Output - second component}\medskip
\end{minipage}
%
\begin{minipage}[b]{0.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{Figures/third}}
%  \vspace{1.5cm}
  \centerline{Output - third component}\medskip
\end{minipage}
%

\caption{Output of a randomly initialized convolution filter.
}
\label{fig:res}
%
\end{figure}

\begin{subsection}{Scaling up Image Classification}
The latest attempt in image classification with an error rate of 5.98\% in ImageNet data set is reported by Ren Wu et al. \cite{Wu2015} of Baidu research. They developed an end to end deep learning  system named Deep Image. It uses a highly optimized parallel algorithm to implement large deep neural network with augmented input data. The network is trained using Stochastic Gradient Descent algorithms (SGD) on a custom built high performance system comprised of 36 server nodes, each with 2 six-core Intel Xeon E5-2620 processors and 4 NVIDIA Tesla K40m GPUs. System  uses an InfiniBand  network for interconnections. Parallelism strategies used in this network are model-data parallelism and data parallelism. These methods have been proposed by Alex Krizhevsky \cite{Krizhevsky2014} and Omry Yadan et al. \cite{Yadan2013} for training convolutional neural networks with SGD on a  multiple GPU systems. However, it is not easy to extend the same strategies to multiple GPU clusters because of the communication overhead. The major objective is to minimize network data transfers and dynamic computation. So it uses butterfly synchronization and lazy update strategies to achieve data parallelism in the gradient computation. These approaches shows that model-data parallelism is better when number of GPUs is less than 16. Implementation of Data parallelism in a large number of GPU cluster is better because of the constant communication requirements.
\par
Data augmentation techniques are used to increase the number of labeled images in the training set. This includes color casting, vignetting, lens distortion, rotation, flipping and cropping. But this data augmentation techniques does not solve the major problems such as occlusion, presence or absence of structural components, and lighting conditions.
\begin{table*}[ht]
\captionsetup{justification=centering,belowskip=-2pt,aboveskip=-2pt}
\caption[]{ Comparative analysis of state-of-the-art deep convolutional network based image classification algorithms using ILSVRC dataset.}
 \begin{tabular}{ | p{2.7cm} | l | p{1.4cm} |p{1.3cm} |p{.8cm} |p{1.3cm} |p{1.1cm} |p{5cm}|}

\end{tabular}
\label{table_cp}
\end{table*}
\par
 Major contribution of this work is the demonstration of tremendous computational power required to  achieve high accuracy in image classification.
It also shows that augmented multi-scale images can be combined to achieve less error rate in convolutional network in the context of the image classification. 
 \end{subsection}
 \section {Observations}
In recent years, the research community has reported several image classification algorithms based on deep convolutional network which gives less rate. A comparative analysis of recent futuristic deep convolutional networks is shown in Table \ref{table_cp}.
  Ren Wu et al. \cite{Wu2015} uses aggressive data argumentation and high computational power to reduce the computational time and error rate. Karen Simonyan et al. \cite{Arge2015} work shows, error rate can be reduced using small convolution filters. Christian Szegedy  et al. \cite{Szegedy} and Min Lin et al. \cite{Lin2013} introduces a set of hidden layers to model local patches. Kaiming He et al. \cite{He2014} uses a different pooling technique to reduce the error rate. Krizhevsky, et al. \cite{Krizhevsky2012a}  introduces  rectifier  as the neuron function. Although significant progress has been made in the last few years, there is still room for further research and improvement. Major observations from our study are listed below.
 \begin{itemize}
 \itemsep0pt 
 \item  Wisely chosen data  augmentation techniques can increase the performance of the network. But need to be tested with multiple data set.
 \item Data parallelism and model parallelism can increase the speed of the training process. This area can be exploited further to increase the speed of the training process.
 \item Greater depth with small convolution filters will improve the accuracy. But, response to different frequency input must be studied.
 \item Performance of the network will get improved if images at difference scales are used for training.
 \item Use of different pooling technique such as spatial pyramid pooling in sub-architectural level may reduce the error rate. 
\end{itemize}
\section{conclusion}
This paper attempts to provide a  review of research on deep convolutional networks  and provide an overview of  its architecture and performance. Majority of the reviewed  works are reported from ImageNet Large-Scale Visual Recognition Challenge. These networks can only be trained using very expensive computing resources such as multiGPU cluster  to achieve more accuracy on large data sets. So  this research heavily depends on other research domains such as parallel algorithms, computer networks and multicore architecture. Because of the heavy computational requirements, it is not easy to apply this method directly  to the small level computing platforms such as embedded systems and application level  processors. On the other side, these methods can easily bring  live with the help of  cloud computing infrastructure, so to the mobility solutions such as mobile phones and the web.

\bibliographystyle{IEEEbib}
\bibliography{refs}

\end{document}

>>>>

% Template for ICIP-2015 paper; to be used with:
\documentclass{llncs}

\usepackage{amsmath,graphicx}
\usepackage{caption}

@@

% Title.
% ------
\title { On Deep Convolutional networks for large scale image classification}

%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%

@@

@@

\bibliographystyle{splncs03.bst}
\bibliography{refs}

\end{document}% Template for ICIP-2015 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------

### 2015-05-12 vslam/odometry/digest.tex
springer template started

\documentclass{article}
\usepackage{setspace}
\usepackage[margin=.8 in]{geometry}
\usepackage{amsmath,graphicx}
\usepackage[font=small,skip=1pt]{caption}
\usepackage{float}
\captionsetup[figure]{font=small,skip=1pt}
\author{\#Authors}
\title{Stereo odometry based on  Local Intensity Order Pattern}
\onehalfspacing
\begin{document}
\maketitle
\begin{abstract}
New generation autonomous vehicles use different data fusion techniques to solve the Simultaneous Localization And Mapping (SLAM) problems in urban terrains.  However, the majority of the implementations uses high-cost sensors like LIDAR to obtain a high accuracy map. In this paper, we  present a novel method  to solve this problem using sequences of stereo images. Our approach uses Local Intensity Order Pattern (LIOP) based  feature descriptors to  overcome the problem of monotonic intensity changes and affine transformations of detected features. Egomotion of the vehicle is estimated using correspondence of features on the consecutive frames. Estimated motion parameters are then corrected using an extended Kalman filter. Depth of the detected features is calculated using stereo triangulation. Mahalanobis distance  is used to avoid outliers in the detected features.
The accuracy of  the proposed method is  evaluated using the measurements from a  high accurate inertial navigation system. Method is tested using the odometry data set of the KITTI Vision Benchmark Suite.

@@

The proposed system is similar to the method suggested by Bernd Kitt et al.\cite{Kitt2010IV}. However, to make the system more robust to illumination changes, specular reflection and blur   LIOP \cite{wang2011local} based  feature descriptors are introduced. To Mahalanobis distance-based outlier rejection \cite{Blanco2012} method is are used to calculate optimal correspondence between the feature points. Shortlisted feature points are projected to 3D with the help of triangulation from the camera baseline to obtain the depth. Estimated camera motion parameters are corrected using   the extended Kalman filter. An overview of the system is given in fig \ref{sv}.
\begin{figure}[ht]
 \centering
 \includegraphics[width=10cm]{images/so.eps}
\caption{System Overview}
\label{sv}
\end{figure}

\subsection{Feature extraction, description and matching }
The performance of a visual odometry system  depends on extraction and representation of features. To achieve a consistent odometry in adverse weather and lighting conditions, the descriptor must be invariant to photometric transforms such as  specular reflections, complex illumination changes and monotonic intensity changes.
However, the widely used descriptors such as Scale Invariant Feature Transform(SIFT) and Gradient Location-Orientation Histogram (GLOH) are robust to geometric transformations but sensitive to  photometric transformations.
\par
The proposed system uses  Local Intensity Order Pattern(LIOP)\cite{wang2011local} based descriptors to encode  the regions detected by the Hessian-affine covariant region detector. In the preprocessing stage, image is smoothed by a Gaussian filter and feature position and shape are identified by the Hessian-affine detector\cite{mikolajczyk2002affine}. Detected regions are normalized to circular areas of fixed diameter. These local patches are sorted based on the intensity level of the pixels and construct a histogram based on the order.

\par
Rotation invariant is achieved by taking neighbourhood pixels of pixel $x$ in the anticlockwise direction on a circle. In order to develop  the histogram, the identified order of intensities in the neighbourhood  of pixels will map to a linear index. Bins are constructed based on the weighted pooling of mapped linear indices  in the region. Extracted features are matched using the fast nearest neighbour matching algorithm. Figure \ref{match} shows randomly selected feature matches .

\begin{figure}[ht]
 \centering
 \includegraphics[width=15cm , height=4cm]{images/matchc.eps}
\caption{LIOP descriptor matches between  left and right images.}
\label{match}
\end{figure}
\subsection{Outlier rejection and State Estimation}
Mahalanobis distance is used to identify the optimal set of the detected feature matches. It is used to calculate the distance between a feature and the overall distribution of the feature correspondence. The Mahalanobis distance \cite{de2000mahalanobis} of an observation $x = ( x_1, x_2, x_3, \dots, x_N )^T$ from a group of observations with mean $\mu = ( \mu_1, \mu_2, \mu_3, \dots , \mu_N )^T$ and covariance matrix $S$ is defined as:

@@

\section{Results and Observations}
Proposed method is tested using KITTI vision benchmark suite\cite{Geiger2012CVPR}  and estimated position  and errors for the sequence-01 are given in figure [3-7]. Algorithms are implemented using C++ with help of VLFEAT library in an  i5-3210M, 2.5Ghz CPU.Following are the observations from this empirical method.

\begin{itemize}
\item Use of LIOP based feature descriptors will improve the accuracy of the estimation, but the computational cost is high. 
\item  LIOP features are invariant to the photometric transformation such as illumination changes. However, It can be further improved in the context of visual odometry.
\end{itemize}
\begin{figure}[ht]
 \centering
 \includegraphics[width=10cm ]{images/01.eps}
\caption{Estimated path.}
\label{match}
\end{figure}
\begin{figure}[H]
    \centering
    \begin{minipage}{.5\textwidth}

        \centering
        \includegraphics[width=8cm]{images/01_rl.eps}
        \vspace{-1.5em}
        \caption{Rotation Error  vs Path Length}
        \label{a}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \centering
        \includegraphics[width=8cm]{images/01_rs.eps}
         \vspace{-1.5em}
        \caption{Rotation Error  vs Speed}
        \label{b}
    \end{minipage}
    \centering
    \begin{minipage}{.5\textwidth}
        \centering
        \includegraphics[width=8cm]{images/01_tl.eps}
         \vspace{-1.5em}
        \caption{Translation Error  vs Path Length}
        \label{c}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \centering
        \includegraphics[width=8cm]{images/01_ts.eps}
         \vspace{-1.5em}
        \caption{Translation Error  vs Speed}
        \label{fd}
    \end{minipage}
\end{figure}
\section{conclusion}
 In this paper, we presented a method to estimate ego-motion using visual odometry. This technique relies on  LIOP based feature detector.
Majority of the data set available to evaluate the system does not include the images in a bad weather condition or night driving. So this method needs to explore further with the help of more challenging image datasets with specular reflections and complex illumination changes.

>>>>

\documentclass{article}
\usepackage{setspace}
\usepackage[margin=.8 in]{geometry}
\usepackage{amsmath,graphicx}
\usepackage[font=small,skip=1pt]{caption}
\usepackage{float}
\usepackage{authblk}
\captionsetup[figure]{font=small,skip=1pt}

\title{Stereo odometry based on  Local Intensity Order Pattern}

\author[1]{Mahesh C.}
\author[1]{Aswathy A. L.}
\author[2]{James Joy}
\affil[1]{Department of Computer Science, University of Kerala, Kariavattom, Thiruvananthapuram-695581,Kerala, India}
\affil[2]{Tata Elxsi Limited, Technopark Campus, Kariavattom, Thiruvananthapuram-695581,Kerala, India}

\date{}
\onehalfspacing
\begin{document}
\maketitle
\begin{abstract}
New generation autonomous vehicles use different data fusion techniques to solve the Simultaneous Localization And Mapping (SLAM) problems in urban terrains.  However, the majority of the implementations uses high-cost sensors like LIDAR to obtain a high accuracy map. In this paper, we  present a method  to solve this problem using sequences of stereo images. Our approach uses Local Intensity Order Pattern (LIOP) based  feature descriptors to  overcome the problem of monotonic intensity changes and affine transformations of detected features. Ego-motion of the vehicle is estimated using correspondence of features on the consecutive frames. Estimated motion parameters are then corrected using an extended Kalman filter. Depth of the detected features is calculated using stereo triangulation. Mahalanobis distance  is used to avoid outliers in the detected features.
The accuracy of  the proposed method is  evaluated using the measurements from a  high accurate inertial navigation system. Method is tested using the odometry data set of the KITTI Vision Benchmark Suite.

@@

The proposed system is similar to the method suggested by Bernd Kitt et al.\cite{Kitt2010IV}. However, to make the system more robust to illumination changes, specular reflection and blur, LIOP \cite{wang2011local} based feature descriptors are introduced. In the preprocessing stage, image is smoothed by a Gaussian filter and feature position and shape are identified by the Hessian-affine detector\cite{mikolajczyk2002affine}. Mahalanobis distance-based outlier rejection \cite{Blanco2012} method is used to calculate optimal correspondence between the feature points. Shortlisted feature points are projected to 3D with the help of triangulation from the camera baseline to obtain the depth. Estimated camera motion parameters are corrected using   the extended Kalman filter. An overview of the proposed system is given in Figure \ref{sv}.
\begin{figure}[ht]
 \centering
 \includegraphics[width=10cm]{images/so.eps}
\caption{System Overview}
\label{sv}
\end{figure}

\subsection{Feature extraction, description and matching }
The performance of a visual odometry system  depends on extraction and representation of features. To achieve a consistent odometry in adverse weather and lighting conditions, the descriptor must be invariant to photometric transforms such as  specular reflections, complex illumination changes and monotonic intensity changes.
However, the widely used descriptors such as Scale Invariant Feature Transform(SIFT) and Gradient Location-Orientation Histogram (GLOH) are robust to geometric transformations but sensitive to  photometric transformations.
\par
The proposed system uses  Local Intensity Order Pattern(LIOP)\cite{wang2011local} based descriptors to encode  the regions detected by the Hessian-affine covariant region detector. Detected regions are normalized to circular areas of fixed diameter. These local patches are sorted based on the intensity level of the pixels and construct a histogram based on the order.

\par
Rotation invariant is achieved by considering a circular disk of neighbourhood pixels of pixel $x$ in the anticlockwise direction on a circle. In order to develop  the histogram, the identified order of intensities in the neighbourhood  of pixels will map to a linear index. Bins are constructed based on the weighted pooling of mapped linear indices  in the region. Extracted features are matched using the fast nearest neighbour matching algorithm. Figure \ref{lmatch} shows randomly selected feature matches .

\begin{figure}[ht]
 \centering
 \includegraphics[width=12cm , height=2.6cm]{images/matchc.eps}
\caption{LIOP descriptor matches between  left and right images.}
\label{lmatch}
\end{figure}
\subsection{Outlier rejection and State Estimation}
Mahalanobis distance is used to identify the optimal set of the detected feature matches. It is used to calculate the distance between a feature and the overall distribution of the feature correspondence. The Mahalanobis distance \cite{de2000mahalanobis} of an observation $x = ( x_1, x_2, x_3, \dots, x_N )^T$ from a group of observations with mean $\mu = ( \mu_1, \mu_2, \mu_3, \dots , \mu_N )^T$ and covariance matrix $S$ is defined as:

@@

\section{Results and Observations}
Proposed method is tested using KITTI vision benchmark suite\cite{Geiger2012CVPR}. Figure \ref{rep} and \ref{res} shows the rotation error of the estimated path. Figure \ref{tep} and \ref{tes} shows the translation error of the estimated path. Estimated path and ground truth are compared in Figure \ref{ep}. Algorithms are implemented using C++ with help of VLFeat  library in an  INTEL i5-3210M, 2.5Ghz CPU. Following are the observations from this empirical method.

\begin{itemize}
\item Use of LIOP based feature descriptors will improve the accuracy of the estimation, but the computational cost is high. 
\item  LIOP features are invariant to the photometric transformation such as illumination changes. However, It can be further improved in the context of visual odometry.
\end{itemize}
\begin{figure}[ht]
 \centering
 \includegraphics[width=9cm ]{images/01.eps}
\caption{Estimated path.}
\label{ep}
\end{figure}
\begin{figure}[H]
    \centering
    \begin{minipage}{.5\textwidth}

        \centering
        \includegraphics[width=8cm]{images/01_rl.eps}
        \vspace{-1.5em}
        \caption{Rotation Error  vs Path Length}
        \label{rep}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \centering
        \includegraphics[width=8cm]{images/01_rs.eps}
         \vspace{-1.5em}
        \caption{Rotation Error  vs Speed}
        \label{res}
    \end{minipage}
    \centering
    \begin{minipage}{.5\textwidth}
        \centering
        \includegraphics[width=8cm]{images/01_tl.eps}
         \vspace{-1.5em}
        \caption{Translation Error  vs Path Length}
        \label{tep}
    \end{minipage}%
    \begin{minipage}{0.5\textwidth}
        \centering
        \includegraphics[width=8cm]{images/01_ts.eps}
         \vspace{-1.5em}
        \caption{Translation Error  vs Speed}
        \label{tes}
    \end{minipage}
\end{figure}
\section{conclusion}
 In this paper, we presented a method to estimate ego-motion using visual odometry. This technique relies on  LIOP based feature detector.
Majority of the data set available to evaluate the system does not include the images in a bad weather condition or night driving. So this method needs to explore further with the help of more challenging image datasets with specular reflections and complex illumination changes.
